### 2020-02-12 README.Rmd
Work in progress, all very rough :construction:
:construction:
Still figuring out interface

<!-- badges: start -->
<!-- badges: end -->

@@

```{r}
library(hashuri)
```

@@

```{r}
hash_uri(vostok_co2)
```

@@

```{r}
co2_url <- "http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2"
register_url(co2_url)
```

@@

```{r}
resolve_hash("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

>>>>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/contenturi)](https://CRAN.R-project.org/package=contenturi)
[![R build status](https://github.com/cboettig/contenturi/workflows/R-CMD-check/badge.svg)](https://github.com/cboettig/contenturi/actions)
<!-- badges: end -->

@@

```{r}
library(contenturi)
```

@@

```{r}
content_uri(vostok_co2)
```

@@

```{r}
co2_url <- "http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2"
remote_register(co2_url)
```

@@

```{r}
remote_lookup("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```
